### 2017-04-03 paper/evaluation.tex

\begin{figure}[ht]
    \centering

    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.38\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/boxplots-testcases.pdf}
      \caption{\label{fig:medtcost}Distribution of test cases per group}
    \end{subfigure}\\
    \vspace{3ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  9 & 14 & 5 \\
        Medium & 17 & 20 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{adjust values}}    
    \end{subfigure}%

    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}    
\end{figure}

\sloppy Figures~\ref{fig:medtcost} and~\ref{fig:longtcost} show the
time distribution of tests per project.  We observed that the average
median value of execution cost for a test was relatively small (dashed
horizontal red lines), namely \Fix{0.41s} for \medg{} projects and
\Fix{0.23s} for \longg{} projects.  Note that correlation between cost
of test suites and cost of their individual tests is not to be
expected.  The standard deviation ($\sigma$) associated with each
distribution was relatively low.  Figure~\ref{fig:sd} shows the number
of projects within specific ranges of $\sigma$ values.  We also
observed that projects with very high standard deviations may or may
not be indicative of monopolization of execution by a small number of
tests.  For example, the highest value of $\sigma$ occurred in project
\CodeIn{wildfly-swarm}, whose test suite was classified as
long-running.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{wildfly-swarm} was an extreme case;
we did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{jenkinsci.gerrit-trigger-plugin} is
also classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119} take more than
\Fix{1s} to run.

>>>>

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=.75\textwidth]{plots/boxplots-testcases.pdf}
        \caption{\label{fig:medtcost}Distribution of test cases.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=.68\textwidth]{plots/scatter-testcost.pdf}
        \caption{\label{fig:scattercost}\Fix{maybe the coordinates should be flipped}}
     \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Long   &  7 & 15 & 12 \\
        Medium & 22 & 19 & 7 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}Standard deviantion of test cases}
    \end{subfigure}%
    \caption{\label{fig:time-distributions}Distribution of test case
    execution cost per project.}%
\end{figure}

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of tests per project.  We observed that the average
median value of execution cost for a test was relatively small (dashed
horizontal red lines), namely 0.31s for \medg{} projects and
0.23s for \longg{} projects.  Note that correlation between cost
of test suites and cost of their individual tests is not to be
expected.  The standard deviation ($\sigma$) associated with each
distribution was relatively low.  Figure~\ref{fig:sd} shows the number
of projects within specific ranges of $\sigma$ values.  We also
observed that projects with very high standard deviations may or may
not be indicative of monopolization of execution by a small number of
tests.  For example, the highest value of $\sigma$ occurred in project
\CodeIn{uber\_chaperone}, whose test suite was classified as
medium-running.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{uber\_chaperone} was an extreme case;
we did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{facebookarchive\_linkbench} is
classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119} take more than
\Fix{1s} to run.
